Carbonate chemistry at Ny-Ålesund

### 2023-01-09 awipev-CO2.Rmd
started figs for paper

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
p_avail <- pivot_longer(z, -Flag) %>% 
  drop_na() %>% 
  ggplot(aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  labs(x="", y="", title = "Distribution (%) of quality flags") +
  Mytheme(size_labs = 8) #+
  theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
kable(z, digits = 1)
# Monthly distribution of hourly data
d2 <- d_all %>% 
  dplyr::select(montht, pco2_fb, phINT)
count_pco2_fb_no_NA <- sum(!is.na(d2$pco2_fb)) # total non-NA pCO2 values
count_phINT_no_NA <-  sum(!is.na(d2$phINT)) # total non-NA pH seafet values
# calculate the distribution of non-NA pCO2 and pH values per month
d2_summary <- d2 %>% 
  dplyr::group_by(montht) %>% 
  dplyr::summarise(pco2 = round(100 * sum(!is.na(pco2_fb))/1000, digits = 1),
                   pH = round(100 * sum(!is.na(phINT))/1000, digits = 1),
                   pco2_pc = round(100 * sum(!is.na(pco2_fb))/count_pco2_fb_no_NA, digits = 1),
                   pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
                   )
# plot the distribution of non-NA pCO2 and pH values per month
p_avail_month <- d2_summary %>% 
  tidyr::pivot_longer(cols = c(pco2, pH)) %>% 
  ggplot() +
  geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
  labs(x="Month", y="Number of data (thousands)", title = "") +
  Mytheme(size_labs = 8) #+
  #theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
# Combine plots
p <- (p_avail / p_avail_month)
p <- p + plot_annotation(tag_levels = 'A')
p
ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")

# deleted unneeded data
rm(x, d_min, list=ls(pattern="^d2"))
```

@@

# for paper
at_s <- d_all_at_discrete %>% 
  dplyr::select(sal_fb_mix, at) %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 0.5) +
  labs(x= latex2exp::TeX("Salinity"),
       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
  coord_fixed()
ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")

@@

# for paper
pco2_calc_meas <- d_all %>% 
  dplyr::select(pco2_fb_insi_temp, pco2_calc_fb_insi_temp) %>% 
  drop_na() %>% 
  ggplot(aes(x = pco2_fb_insi_temp, y = pco2_calc_fb_insi_temp)) +
  geom_point(col="blue", size = 0.5) +
  xlim(180, 420) + ylim(180, 420) +
  labs(x=latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pco2_calc_meas.png", plot = pco2_calc_meas, width = 25, height = 25, units = "cm")
```

@@

offset_ph <- ph_sf %>% 
  drop_na() %>% 
  ggplot() +
  geom_point(aes(x=datetime, y=diff_spec_sf), size=1, color="blue") +
  geom_hline(yintercept=0, size=0.3) +
  geom_hline(yintercept=-0.02, size=0.3, linetype = "dashed") +
  geom_hline(yintercept=0.02, size=0.3, linetype = "dashed") +
  labs(x = "Date", y=expression(paste(pH[T], " difference")), title = NULL) +
  Mytheme(size_labs = 9, face_font = "plain") + theme(aspect.ratio=1)  + 
  scale_colour_discrete(guide="none") + 
  coord_fixed()
ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 25, height = 25, units = "cm")
```

@@

pHspec_pHseafet <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
  drop_na() %>% 
  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
  geom_point(col="blue", size = 0.5) +
  xlim(8.05, 8.18) + ylim(8.05, 8.18) +
  labs(x="Spectrophotometric pH",
       y= "SeaFET pH")  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pHspec_pHseafet.png", plot = pHspec_pHseafet, width = 25, height = 25, units = "cm")
```

@@

p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  geom_hline(yintercept = 0) +
  labs(title = "", x = "", y= "") +
  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
  Mytheme(size_labs = 10)
# diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
# fct_relevel(diff_all_long$variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite')

# calculate descriptive statistics
diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls$delta_ph)),
                        CT = as.numeric(summary(diff_ls$delta_ct * 1e6)),
                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lp_quant <- tibble(pH = as.numeric(summary(diff_lp$delta_ph)),
                        CT = as.numeric(summary(diff_lp$delta_ct * 1e6)),
                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lm_quant <- tibble(pH = as.numeric(summary(diff_lm$delta_ph)),
                        CT = as.numeric(summary(diff_lm$delta_ct * 1e6)),
                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)

ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
```

@@

p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  geom_hline(yintercept = 0) +
  labs(title = "", x = "", y= "") +
  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
  Mytheme(size_labs = 10)

# calculate descriptive statistics
diff_ls2_quant <- tibble(pH = as.numeric(summary(diff_ls2$delta_ph)),
                        pCO2 = as.numeric(summary(diff_ls2$delta_pCO2)),
                        OmegaAragonite = as.numeric(summary(diff_ls2$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lp2_quant <- tibble(pH = as.numeric(summary(diff_lp2$delta_ph)),
                        pCO2 = as.numeric(summary(diff_lp2$delta_pCO2)),
                        OmegaAragonite = as.numeric(summary(diff_lp2$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lm2_quant <- tibble(pH = as.numeric(summary(diff_lm2$delta_ph)),
                        pCO2 = as.numeric(summary(diff_lm2$delta_pCO2)),
                        OmegaAragonite = as.numeric(summary(diff_lm2$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
# boxplot
ggsave(filename = "figures/k1k2_ct_at.png", plot = p, width = 25, height = 20, units = "cm")

# prepare tibble to compare calculated pH and spec pH
tmp2 <- tibble(datetime = tmp$datetime, ph_s_dur_temp_4_l = tmp$ph_s_dur_temp_4_l, 
               ph_s_dur_temp_4_s20 = tmp$ph_s_dur_temp_4_s20,
               ph_s_dur_temp_4_p18 = tmp$ph_s_dur_temp_4_p18,
               ph_s_dur_temp_4_m02 = tmp$ph_s_dur_temp_4_m02, 
               pH_l2 = carb_l2$pH, pH_s2 = carb_s2$pH, 
               pH_p2 = carb_p2$pH, pH_m2 = carb_m2$pH, temp_fb = tmp$temp_fb) %>% 
  tidyr::drop_na(ph_s_dur_temp_4_l)
# summary of differences
lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4_l - tmp2$pH_l2))
sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s2))
papadimitriou <- as.numeric(summary(tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p2))
millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m2))
diff_table_at_ct <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
# make plots
p1 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_l2, type = "MA", plot = TRUE, 
            title = "Lueker vs measured", subtitle = "both pH normalized at 4°C",
            xlab = "Spectrophotometric pH normalized @ 4°C",
            ylab = "pH @ 4°C calculated (AT+CT) with Lueker",
            proplot = TRUE)$plot +
  lims(x = c(8, 8.4), y = c(8, 8.4)) +
  theme(plot.title = element_text(size = 10),
        axis.text = element_text(size = 10))
p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_s2, type = "MA", plot = TRUE, 
            title = "Sulpis vs measured", subtitle = "both pH normalized at 4°C",
            xlab = "Spectrophotometric pH normalized @ 4°C",
            ylab = "pH @ 4°C calculated (AT+CT) with Sulpis",
            proplot = TRUE)$plot  +
  lims(x = c(8, 8.4), y = c(8, 8.4)) +
  theme(plot.title = element_text(size = 10),
        axis.text = element_text(size = 10)) +
  coord_fixed(ratio = 1)
p3 <- tmp2 %>% 
  dplyr::mutate(delta_lueker = tmp2$ph_s_dur_temp_4_l - tmp2$pH_l2, 
                delta_sulpis = tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s2, 
                delta_papadimitriou = tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p2, 
                delta_millero2002 = tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m2) %>% 
  dplyr::select(-starts_with("ph_"), -datetime) %>% 
  tidyr::pivot_longer(!temp_fb, names_to = "delta", values_to = "diff") %>% 
  ggplot(aes(x = temp_fb, y = diff, col = delta)) +
  geom_point() + geom_line() +
  labs(x = "Ferrybox temperature (°C)", y = "Spec pH - calculated pH (units)") +
  theme(legend.title = element_blank())
p <- (p1 + p2) / p3
ggsave(filename = "figures/k1k2_discrete_at_ct.png", plot = p, width = 25, height = 20, units = "cm")

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
g <- g + patchwork::plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
g
```

>>>>

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
p_avail <- pivot_longer(z, -Flag) %>% 
  drop_na() %>% 
  ggplot(aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  scale_x_discrete(
    labels = c(
      "Flag",
      'pCO2' = parse(text = TeX('$pCO_2$')),
      "Salinity FerryBox",
      "In situ salinity",
      "Temperature FerryBox",
      "In situ temperature",
      "Durafet pH",
      "seaFET pH"
    )
  ) +
  coord_flip() +
  labs(x="", y = "Distribution of quality flags (%)") +
  Mytheme(size_labs = 12) +
  theme(legend.title = element_text(colour="black", size=12, face="bold")) #+
  #theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
#kable(z, digits = 1)
d2 <- d_all %>% 
  dplyr::select(montht, pco2_fb, phINT)
count_pco2_fb_no_NA <- sum(!is.na(d2$pco2_fb)) # total non-NA pCO2 values
count_phINT_no_NA <-  sum(!is.na(d2$phINT)) # total non-NA pH seafet values
# calculate the distribution of non-NA pCO2 and pH values per month
d2_summary <- d2 %>% 
  dplyr::group_by(montht) %>% 
  dplyr::summarise(pco2 = round(100 * sum(!is.na(pco2_fb))/1000, digits = 1),
                   pH = round(100 * sum(!is.na(phINT))/1000, digits = 1),
                   pco2_pc = round(100 * sum(!is.na(pco2_fb))/count_pco2_fb_no_NA, digits = 1),
                   pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
                   )
# plot the distribution of non-NA pCO2 and pH values per month
p_avail_month <- d2_summary %>% 
  tidyr::pivot_longer(cols = c(pco2, pH)) %>% 
  ggplot() +
  geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
  scale_fill_discrete(name = "", labels = c(expression(paste(pCO[2])), "pH")) + 
  labs(x="Month", y="Number of data (thousands)", title = "") +
  Mytheme(size_labs = 12) #+
# Combine plots
p <- (p_avail / p_avail_month)
p <- p + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")
ggsave(filename = "figures/essd/fig01.pdf", plot = p, width = 20, height = 15, units = "cm")

# deleted unneeded data
#rm(x, d_min, list=ls(pattern="^d2"))
```

@@

# for paper
at_s <- d_all_at_discrete %>% 
  dplyr::select(sal_fb_mix, at) %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 1) +
  labs(x= latex2exp::TeX("Salinity"),
       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio=1) + 
  coord_fixed()
ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")

@@

# for paper
pco2_calc_meas <- d_all %>% 
  dplyr::select(pco2_fb_insi_temp, pco2_calc_fb_insi_temp) %>% 
  drop_na() %>% 
  ggplot(aes(x = pco2_fb_insi_temp, y = pco2_calc_fb_insi_temp)) +
  geom_point(col="blue", size = 1) +
  xlim(180, 420) + ylim(180, 420) +
  labs(x=latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pco2_calc_meas.png", plot = pco2_calc_meas, width = 25, height = 25, units = "cm")
```

@@

offset_ph <- ph_sf %>% 
  drop_na() %>% 
  ggplot() +
  geom_point(aes(x=datetime, y=diff_spec_sf), size=1, color="blue") +
  geom_hline(yintercept=0, size=0.3) +
  geom_hline(yintercept=-0.02, size=0.3, linetype = "dashed") +
  geom_hline(yintercept=0.02, size=0.3, linetype = "dashed") +
  labs(x = "Date", y=expression(paste(pH[T], " difference")), title = NULL) +
  Mytheme(size_labs = 12, face_font = "plain") + theme(aspect.ratio=1)  + 
  scale_colour_discrete(guide="none") + 
  coord_fixed()
ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 25, height = 25, units = "cm")
```

@@

pHspec_pHseafet <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
  drop_na() %>% 
  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
  geom_point(col="blue", size = 1) +
  xlim(8.05, 8.18) + ylim(8.05, 8.18) +
  labs(x="Spectrophotometric pH",
       y= "SeaFET pH")  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pHspec_pHseafet.png", plot = pHspec_pHseafet, width = 25, height = 25, units = "cm")
```

@@

p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "blue", outlier.size = 1) +
  geom_hline(yintercept = 0) +
  labs(title = "", x = "", y= "") +
  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
  Mytheme(size_labs = 12)
# calculate descriptive statistics
diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls$delta_ph)),
                        CT = as.numeric(summary(diff_ls$delta_ct * 1e6)),
                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lp_quant <- tibble(pH = as.numeric(summary(diff_lp$delta_ph)),
                        CT = as.numeric(summary(diff_lp$delta_ct * 1e6)),
                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lm_quant <- tibble(pH = as.numeric(summary(diff_lm$delta_ph)),
                        CT = as.numeric(summary(diff_lm$delta_ct * 1e6)),
                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)

ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
ggsave(filename = "figures/essd/fig02.pdf", plot = p, width = 25, height = 20, units = "cm")

@@

p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "blue", outlier.size = 1) +
  geom_hline(yintercept = 0) +
  labs(title = "", x = "", y= "") +
  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
  Mytheme(size_labs = 12)
# calculate descriptive statistics
diff_ls2_quant <- tibble(pH = as.numeric(summary(diff_ls2$delta_ph)),
                        pCO2 = as.numeric(summary(diff_ls2$delta_pCO2)),
                        OmegaAragonite = as.numeric(summary(diff_ls2$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lp2_quant <- tibble(pH = as.numeric(summary(diff_lp2$delta_ph)),
                        pCO2 = as.numeric(summary(diff_lp2$delta_pCO2)),
                        OmegaAragonite = as.numeric(summary(diff_lp2$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
diff_lm2_quant <- tibble(pH = as.numeric(summary(diff_lm2$delta_ph)),
                        pCO2 = as.numeric(summary(diff_lm2$delta_pCO2)),
                        OmegaAragonite = as.numeric(summary(diff_lm2$delta_OmegaAragonite))) %>%
  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
# boxplot
ggsave(filename = "figures/k1k2_ct_at.png", plot = p, width = 25, height = 20, units = "cm")
ggsave(filename = "figures/essd/fig03.pdf", plot = p, width = 25, height = 20, units = "cm")
# prepare tibble to compare calculated pH and spec pH
tmp2 <- tibble(datetime = tmp$datetime, ph_s_dur_temp_4_l = tmp$ph_s_dur_temp_4_l, 
               ph_s_dur_temp_4_s20 = tmp$ph_s_dur_temp_4_s20,
               ph_s_dur_temp_4_p18 = tmp$ph_s_dur_temp_4_p18,
               ph_s_dur_temp_4_m02 = tmp$ph_s_dur_temp_4_m02, 
               pH_l2 = carb_l2$pH, pH_s2 = carb_s2$pH, 
               pH_p2 = carb_p2$pH, pH_m2 = carb_m2$pH, temp_fb = tmp$temp_fb) %>% 
  tidyr::drop_na(ph_s_dur_temp_4_l)
# summary of differences
lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4_l - tmp2$pH_l2))
sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s2))
papadimitriou <- as.numeric(summary(tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p2))
millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m2))
diff_table_at_ct <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
# make plots
p1 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_l2, type = "MA", plot = TRUE, 
            title = "Lueker vs measured", subtitle = "both pH normalized at 4°C",
            xlab = "Spectrophotometric pH normalized @ 4°C",
            ylab = "pH @ 4°C calculated (AT+CT) with Lueker",
            proplot = TRUE)$plot +
  lims(x = c(8, 8.4), y = c(8, 8.4)) +
  theme(plot.title = element_text(size = 10),
        axis.text = element_text(size = 10))
p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_s2, type = "MA", plot = TRUE, 
            title = "Sulpis vs measured", subtitle = "both pH normalized at 4°C",
            xlab = "Spectrophotometric pH normalized @ 4°C",
            ylab = "pH @ 4°C calculated (AT+CT) with Sulpis",
            proplot = TRUE)$plot  +
  lims(x = c(8, 8.4), y = c(8, 8.4)) +
  theme(plot.title = element_text(size = 10),
        axis.text = element_text(size = 10)) +
  coord_fixed(ratio = 1)
p3 <- tmp2 %>% 
  dplyr::mutate(delta_lueker = tmp2$ph_s_dur_temp_4_l - tmp2$pH_l2, 
                delta_sulpis = tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s2, 
                delta_papadimitriou = tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p2, 
                delta_millero2002 = tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m2) %>% 
  dplyr::select(-starts_with("ph_"), -datetime) %>% 
  tidyr::pivot_longer(!temp_fb, names_to = "delta", values_to = "diff") %>% 
  ggplot(aes(x = temp_fb, y = diff, col = delta)) +
  geom_point() + geom_line() +
  labs(x = "Ferrybox temperature (°C)", y = "Spec pH - calculated pH (units)") +
  theme(legend.title = element_blank())
p <- (p1 + p2) / p3
ggsave(filename = "figures/k1k2_discrete_at_ct.png", plot = p, width = 25, height = 20, units = "cm")

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
g <- g + patchwork::plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
ggsave(filename = "figures/essd/fig04.pdf", plot = g)
```
